Project 1 Checkpoint

### 2015-02-03 project1/checkpoint/main.tex
Adding the software simulation section

\section{Simulation Software Architecture}
The simulation software attempts to utilize

>>>>

\section{Simulation Software Architecture}
Because of the event-driven architecture, the system can be though of as a set of event emitters and event listeners.
In some cases, an object may both emit and listen for events.

The first event emitter to consider is the \texttt{CarEmitter}. The \texttt{CarEmitter} uses the measured input
distribution we have for cars and generates a set of cars randomly. It then emits these cars as individual
\texttt{car:arrived} event. There will generally be two \texttt{CarEmitter}s, one for the North and South direction.

The second emitter will be the \texttt{LightSignal}. It will emit \texttt{light:changed} events, passing the light color.
Also, instead of enqueueing these events upfront, it will also listen for \texttt{light:changed} so that its
changing duration can modified on the fly (using the UI).

The \texttt{IntersectionQueue} holds a list of cars lined up at the intersection. It also maintains the
current signal state, so that it can send cars directly through the intersection if the light is green. It responds
to pretty much every event mentioned above. When the light changes, it will need update it's current signal state.
This may mean sending some cars off of the queue and stop holding cars, or to no longer let cars through and make them
wait. Furthermore, when a car arrives it will handle that event by deciding whether the car can pass through or needs
to wait on the light. Also, this class emits events. Whenever a car finally crosses the intersection, it emits
a \texttt{car:exited} event.

Since we want to gather metrics regarding the throughput of cars, we'll also provide a listener class
\texttt{ThroughputStatistics} that will listen for cars to complete their journey through the system. This will
be reported in the UI in real time.
